Choose a License

### 2024-12-04 choose_license.qmd
Add a few resources on licensing

Note, that for data there is, at least in principle, the possibility that a different license applies to the individual entries than to the collective database. For example, if you were to create a database of artworks by others, those artworks would be licensed individually as chosen by the artists, but the license for the database as a whole could be chosen by you. The latter includes the selection of entries, field names and any _sui generis_ database rights. However, if the content was created by you, we recommend you to choose the same license for both content and database. Factual data (like measurements or metadata) should be licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) -- otherwise, consult @nte-other-work-types for some caveats.

@@

As indicated before, a free/open license must allow creating derivative works and must allow exercising the rights granted by it _for any purpose_, including commercial use. There are a few good resources on the reasoning behind that [e.g., see @Klimpel2013; @ODI2015; @Stallman2022NoLimit; @Moller2023], but we would like to highlight one reason in particular.

@@

You may have noticed that we mostly refer to licenses using a name _and_ a version number. This is because the organizations that created the licenses sometimes publish updated versions to accommodate for developments in copyright law and the communities that use the licenses. For example, the Creative Commons licenses (that start with `CC`) were first published in 2002. Since then, the possibility to relicense under compatible licenses has been added ([v3.0](https://creativecommons.org/2007/02/23/version-30-launched/)), a 30-day window to correct license violations has been established to combat [copyleft trolls](https://commons.wikimedia.org/wiki/Commons:Copyleft_trolling), and _sui generis_ database rights are covered explicitly ([v4.0](https://creativecommons.org/version4/)). There are many more [subtle differences between license versions](https://wiki.creativecommons.org/wiki/License_Versions), therefore it is important to indicate which license version exactly one is referring to, as the license of a work does not "update" automatically.

>>>>

Note, that for data there is, at least in principle, the possibility that a different license applies to the individual entries than to the collective database. For example, if you were to create a database of artworks by others, those artworks would be licensed individually as chosen by the artists, but the license for the database as a whole could be chosen by you. The latter includes the selection of entries, field names and any _sui generis_ database rights. However, if the content was created by you, we recommend you to choose the same license for both content and database. Factual data (like measurements or metadata) should be licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) [@Villa2016Copyleft; @Villa2016CC0] -- otherwise, consult @nte-other-work-types for some caveats.

@@

As indicated before, a free/open license must allow creating derivative works and must allow exercising the rights granted by it _for any purpose_, including commercial use. There are a few good resources on the reasoning behind that [e.g., see @Klimpel2013; @ODI2015; @Stallman2022NoLimit; @Moller2023; @Vezina2020; @WikimediaCommons2009], but we would like to highlight one reason in particular.

@@

You may have noticed that we mostly refer to licenses using a name _and_ a version number. This is because the organizations that created the licenses sometimes publish updated versions to accommodate for developments in copyright law and the communities that use the licenses. For example, the Creative Commons licenses (that start with `CC`) were first published in 2002. Since then, the possibility to relicense under later ([v2.0](https://creativecommons.org/2004/05/25/announcingandexplainingournew20licenses/#:~:text=Share%20Alike%20Across%20Borders)) and compatible licenses ([v3.0](https://creativecommons.org/2007/02/23/version-30-launched/)) has been added, a 30-day window to correct license violations has been established to combat [copyleft trolls](https://commons.wikimedia.org/wiki/Commons:Copyleft_trolling), and _sui generis_ database rights are covered explicitly ([v4.0](https://creativecommons.org/version4/)). There are many more [subtle differences between license versions](https://wiki.creativecommons.org/wiki/License_Versions), therefore it is important to indicate which license version exactly one is referring to, as the license of a work does not "update" automatically.
